Appendix

### 2020-05-17 appendixupdates/appendix_final.Rmd
moving file

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
header-includes:
- \usepackage{booktabs}
- \usepackage{longtable}
- \usepackage{array}
- \usepackage{multirow}
- \usepackage{wrapfig}
- \usepackage{float}
- \usepackage{colortbl}
- \usepackage{pdflscape}
- \usepackage{tabu}
- \usepackage{threeparttable}
- \usepackage{threeparttablex}
- \usepackage[normalem]{ulem}
- \usepackage{makecell}
- \usepackage{xcolor}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}

output: pdf_document
---

```{=latex}
\tableofcontents
```

@@

@@

### Search terms

XXXX

### Searched databases

XXXX To Catarina: name and URL of database searched

### Summary total results

XXXX To Catarina: put here results per database, cross-matching, anything else

### Exclusion criteria

#### Exclusion title and abstract

XXXX To Catarina: what criteria for first round exclusions?

#### Exclusion reading

XXXX To Catarina: criteria second round exclusions

@@

For the articles that passed the first two filters, we looked into the tables and the reported coefficients. We kept articles in this step based on two criteria:

@@

### PRISM

- Number of articles matching the search criteria: XXXX
- Number of articles excluded after title and abstract: XXXX
- Number of articles excluded after reading: XXXX
- Number of articles excluded before analysis: 3
- Number of articles excluded during the analysis: 0

We have 26 articles in the meta-analysis.

@@

## Adding articles

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 'readxl',
          'knitr', 'gridGraphics', 'gridExtra','ggpubr','kableExtra','magick')

# Knitr options
knitr::opts_chunk$set(fig.pos = 'H') # holds figure position

@@

\newpage
### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published study?",
       y = "") + 
  theme_bw()

\newpage
### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
dat %>%
  mutate(depvar2 = factor(depvar2, 
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") + 
  labs(x = "Dependent Variables",
       y = "") + 
  coord_flip() + 
  theme_bw()

\newpage
### Independent variables

@@

\newpage
### Histogram Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Coefficients"}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") + 
  labs(x = "Coefficients") + 
  theme_bw()

\newpage
### Histogram Standard Errors

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Histogram Standard Errors"}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") + 
  labs(x = "Standard Errors") + 
  theme_bw()

\newpage
### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign?"}
dat %>%
  ggplot(aes(x=as.factor(scoef))) + 
  geom_bar(color = "black") + 
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n would pose that we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. For the number of legislators in the lower house (N), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'N')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample. For the number of legislators in the upper house (K), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2 == 'K')
binom.test(table(aux$scoef)[1], sum(table(aux$scoef)), p=0.5)
```

@@

\newpage
### Electoral system

@@

\newpage
### Electoral system x Sign Coefficient

@@

\newpage
### ExpPC x K

@@

```{r, echo=FALSE, fig.width=20, fig.height=5}

@@

@@

\newpage
## Meta-regressions

### Meta-regressions for Expenditure measured as

@@

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs = bind_rows(
  mod1,
  mod2,
  mod3,
  mod4,
  mod5) %>%
  select(` `) %>%
  distinct()

aux = list(mod3, mod5, mod1) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4, mod6, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2,-pval)

@@

\blandscape

## Summary of Results
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

```
\elandscape

```{r, echo=F, warning=F,error=F,message=F}
coefs = bind_rows(
  mod1_permu,
  mod2_permu,
  mod3_permu,
  mod4_permu,
  mod5_permu) %>%
  select(` `) %>%
  distinct()

aux = list(mod3_permu, mod5_permu, mod1_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "Base") %>%
  select(mod, everything())

aux2 = list(mod4_permu, mod6_permu, mod2_permu) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_cols) %>%
  mutate(order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "AggLevel: States", 9, order),
         pval = ifelse(`P-Value` < 0.05, "*", NA),
         pval = ifelse(`P-Value` < 0.01, "**", pval),
         pval = ifelse(`P-Value` < 0.01, "***", pval),
         pval = ifelse(`P-Value` >= 0.05, " ", pval),
         `P-Value` = pval) %>%
  arrange(order) %>%
  select(-` 1`, -` 2`, -contains("model"), -order) %>%
  mutate(mod = "All Coefs") %>%
  select(mod, everything())

aux <- bind_rows(aux, aux2) %>%
  select(-contains("CI"),-`T`,-T1,-T2,-pval)

@@

\blandscape

## Summary of Results (Permutation)
```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        " ",
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value",
        #
        "Estimate",
        "SE",
        "P-Value"
      )) %>% 
  collapse_rows(
    1:2,
    row_group_label_position ='stack'
    ) %>%
  add_header_above(c(" ", " ","ExpPC" = 3, "logExpPC" = 3, "PCTGDP" = 3)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

```
\elandscape

>>>>

---
title: "Appendix"
author: "Umberto Mignozzetti"
date: "12/25/2019"
header_includes:
- \usepackage{booktabs}
- \usepackage{pdflscape}
- \newcommand{\blandscape}{\begin{landscape}}
- \newcommand{\elandscape}{\end{landscape}}
output: pdf_document
urlcolor: blue
---

@@

# Needed packages
pkgs <- c('tidyverse', 'meta', 'metafor', 
          'readxl', 'compareGroups',
          'knitr', 'gridGraphics', 'gridExtra',
          'ggpubr','kableExtra','magick')

@@

The first step in reviews is to gather a sample of records. This initial procedure is the foundation for the entire meta-analytical process: if the goal is to aggregate all the available data on a given topic, the primary pool must contain all of it. At the same time, the sample should be concise enough to optimise the work flow. Upon selecting the online databases, we attempted to do a "term" search, based on a set of words we scouted from the distributive politics literature we already knew. This search produced oversized databases, of which a large share was completely unrelated to our subject of investigation. The strategy we found to be the most thorough and productive was to select the records that cited Weingast, Shepsle and Johnsen's 1981 paper "The political economy of benefits and costs: A neoclassical approach to distributive politics". Although \href{https://scholar.google.com/}{Google Scholar} reports the article amounts to \href{https://scholar.google.com/scholar?um=1&ie=UTF-8&lr&cites=13117579863846712459}{2,180} citations\footnote{As of May 11\textsuperscript{th}, 2020.}, as of the 21\textsuperscript{st} of November 2019, our search resulted in a total of 2,664 records.

We webscraped the main databases in Social Sciences: \href{https://scholar.google.com/}{Google Scholar} (n = 1001); \href{https://academic.microsoft.com/home}{Microsoft Academic} (n = 927); and
\href{https://www.scopus.com/}{Scopus} (n = 736). The R script we wrote extracted, to a .csv file, the title, abstract, authors, year, journal of publication, and database from which the record originated. We screened these results with an English language and Article restriction -- meaning, we excluded all records written in other languages and all that were not academic papers, such as book chapters, doctoral theses, etc. We set no restriction to unpublished articles.

Below, you will find the webscrape script:

``` {r, eval = FALSE}

#### PACKAGES ####

# Needed packages
pkgs <- c('tidyverse', 'rvest', 'RSelenium')

#### SETTING UP SELENIUM ####

# Alternative 1: Setting up Selenium (head)
rsD <- rsDriver(port = 1114L, browser = c("firefox")) 
remDr <- rsD$client
remDr$open()

#### Google scholar ####

# site: https://scholar.google.com

remDr$navigate("https://scholar.google.com/
               scholar?cites=13117579863846712459&as_sdt=2005&sciodt=0,5")

articles_weingast <- tibble(
  value = NA,
  term = NA,
  page = NA
)

k <- 0

for (j in 1:213) { # we had to manually choose the number of pages here; Y.M.M.V.

  Sys.sleep(rpois(1, 5))

  # Getting articles basic information
  k <- k + 1

  webElem <- remDr$findElement("css", "body")

  title <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(
      xpath = '//*[contains(concat( " ", @class, " " ),
      concat( " ", "gs_rt", " " ))]'
      ) %>%
    html_text() %>%
    enframe(name = NULL) %>%
    rename("title" = "value") %>%
    mutate(page = k)

  articles_partial <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(xpath = '//*[contains(concat( " ", @class, " " ), concat( " ", "gs_a", " " ))]') %>%
    html_text() %>%
    enframe(name = NULL) %>%
    bind_rows(
      tibble(
        value = "delete",
        term = NA,
        page = NA
      ),
      .
    ) %>%
    bind_cols(., title)

  # Binding articles
  articles_weingast <- bind_rows(articles_weingast, articles_partial)

  # Changing Pages
  next_button <- remDr$findElement(using = "xpath", "/html/body/div/div[11]/div[2]/div[2]/div[3]/
                                   div[2]/center/table/tbody/tr/td[12]/a/b")
  next_button$clickElement()

  # Deleting cookies
  remDr$deleteAllCookies()
}

write_csv(articles_weingast, "scholar_weingast_raw.csv")

articles_weingast <- articles_weingast %>%
  select(-term, -page) %>%
  filter(value != "delete") %>%
  slice(2:nrow(.)) %>%
  filter(!grepl("books.google.com", value)) %>%
  filter(!grepl("BOOK", title)) %>%
  separate(., value, into = c("author", "value"),
           sep = " -", remove = T, extra = "merge", fill = "right") %>%
  separate(., value, into = c("journal", "year"),
           sep = ",", remove = T, extra = "merge", fill = "right") %>%
  mutate(
    year_2 = ifelse(is.na(year), journal, year),
    journal = ifelse(is.na(year), NA, journal),
    year = year_2
  ) %>%
  select(-year_2) %>%
  separate(., year, into = c("year", "site"),
           sep = "-", remove = T, extra = "merge", fill = "right") %>%
  mutate(
    year = gsub("[^0-9 ]", "", value),
    year = gsub("^[0-9]{5,}", "", year),
    year = gsub("^ {1,}", "", year)
  ) %>%
  separate(., year, into = c("year", "junk"),
           sep = " ", remove = T, extra = "merge", fill = "right") %>%
  separate(., value, into = c("journal", "value"),
           sep = "-", remove = T, extra = "merge", fill = "right") %>%
  mutate(
    journal_untidy = year,
    year = gsub("[^0-9 ]", "", year)
  )

articles <- articles %>%
  na.omit() %>%
  distinct(., value, .keep_all = T)

write_csv(articles, "google_scholar_clean.csv")

#### SCOPUS ####

# url: https://www.scopus.com/home.uri

# Scraping Scopus requires a bit more manual labor.
# You can login on scopus through your university/institution and download the metadata
#o fthe article(s) you want directly from there.
# All we need to do after that is scrape the information of
# every link from the .csv file downloaded previously

scopus <- read_csv("scopus.csv")

scopus <- scopus %>%
  mutate(article = map_chr(Link, ~ {
    remDr$navigate(.x)
    read_html(remDr$getPageSource()[[1]]) %>%
      html_nodes(xpath = '//*[(@id = "abstractSection")]//p') %>%
      html_text() %>%
      paste(., collapse = "\r\n")
  })) %>%
  mutate(
    article = gsub(
      '\r\n\nUse this section.*Topics\n\n\n"',
      "",
      article
    ),
    article = gsub(
      "Topics are unique.*onwards.",
      "",
      article
    ),
    article = gsub(
      "Use this section.*documents.",
      "",
      article
    ),
    article = gsub(
      "Learn more about these Topics",
      "",
      article
    ),
    article = gsub(
      ". 20.*, Springer Science\\+Business Media, LLC, part of Springer Nature.",
      "",
      article
    ),
    article = gsub("\r", "", article),
    article = gsub("\n", "", article),
    article = gsub(" {2,}", " ", article),
    article = gsub(" {3,}", "", article)
  )

write_csv(scopus, "scopus_clean.csv")

#### Microsoft Academic ####

# url: https://academic.microsoft.com/home

articles <- list()
k <- 0
remDr$navigate("https://academic.microsoft.com/paper/
               2076316673/citedby/search?q=The%20Political%
               20Economy%20of%20Benefits%20and%20Costs%3A%20A%
               20Neoclassical%20Approach%20to
               %20Distributive%20Politics&qe=RId%253D2076316673&f=&orderBy=0")

# 1) Getting hyperlinks from articles
for (j in 1:100) {
  k <- k + 1
  print(k)

  # Navigating Website

  Sys.sleep(rpois(2, 5))

  # Getting articles' links
  articles[[k]] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(xpath = "//a") %>%
    html_attr("href") %>%
    enframe(name = NULL) %>%
    filter(
      grepl("paper/", value),
      !grepl("citedby", value)
    ) %>%
    mutate(value = paste0("https://academic.microsoft.com/", value))

  # Changing Page
  next_page_others <- remDr$findElement(using = "xpath", "/html/body/div/div/div/router-view/router-view/                                        ma-edp-serp/div/div[2]/div/
  compose/div/div[2]/ma-pager/div/i[2]")
  next_page_others$clickElement()
}

articles <- articles %>%
  reduce(bind_rows) %>%
  distinct(value, .keep_all = T)

# 2) Navigating through articles and scraping them

articles_links <- articles %>%
  mutate(
    abstract = NA,
    title = NA,
    year = NA,
    journal = NA,
    authors = NA,
    tags = NA
  )

for (i in 1:nrow(articles_links)) {
  remDr$navigate(articles_links$value[i])
  Sys.sleep(rpois(1, 4))

  articles_links$abstract[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = "//html/body/div/div/div/router-view/compose[1]/
               div/div/ma-entity-detail-info/compose/div/div/div[1]/p") %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$title[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(.,
               xpath = '//*[contains(concat( " ", @class, " " ),
               concat( " ", "name", " " ))]') %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$year[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., 
               xpath = '//*[contains(concat( " ", @class, " " ),
               concat( " ", "name-section", " " ))]
               //*[contains(concat( " ", @class, " " ), concat( " ", "year", " " ))]') %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$journal[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = '//*[contains(concat( " ", @class, " " )
               , concat( " ", "pub-name", " " ))]') %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$authors[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/div/div/
               ma-entity-detail-info/compose/div/div/div[1]/
               ma-author-string-collection") %>%
    html_text() %>%
    paste(., collapse = " ")

  articles_links$tags[i] <- read_html(remDr$getPageSource()[[1]]) %>%
    html_nodes(., xpath = "/html/body/div/div/div/router-view/compose[1]/
               div/div/ma-entity-detail-info/compose/
               div/div/div[1]/ma-tag-cloud/div") %>%
    html_text() %>%
    paste(., collapse = " ")
}

write_csv(articles_links, "microsoft_academic_clean.csv")

## Article Selection

The selection process was conducted by two authors in three phases. In the first round, we excluded all titles that were obviously unrelated to our topic of investigation. For instance, we curiously found articles about automobile motors amidst our sample. We consider this a preliminary step, since we were not able to eliminate a large number of entries. Thus, we read all abstracts. We chose to maintain those that indicated either government expenditure or legislative structures were central matters. For instance, if the paper sought to identify variables that increased government size, it was maintained. Abstracts that indicated the paper discussed or estimated the impacts of representative institutions, elections, or chamber dynamics, for example, were also included. This allowed us to significantly reduce our sample to 376 records.

In the second phase, we assessed full-texts. To proceed, the paper should (i) conduct a quantitative analysis, (ii) report data on the number of legislators, and (iii) also on public expenditure. If the record was marked as positive for all three, it was maintained. Disagreements in this phase were discussed among the authors, and a third was consulted when needed.

The third phase consisted of filling out tables for each of the remaining 50 articles to systematically evaluate their eligibility. Since government spending and the number of parliamentaries assume the form of different variables, we extracted the coefficients that provided this information in all papers, indicating and defining which variables each author used. By observing what is most commonly used, we could decide which variables we would employ in our analysis. In this phase, we also collected information on whether or not the paper had been published, and if it explicitly discussed the \textit{law of 1/n}. Upon choosing the variables, we excluded the non-conforming studies, arriving at our final sample of 26 articles.

@@

We selected the final pool of articles based on two criteria regarding their reported coefficients:

@@

### Flow Chart

We visually organised the flow of articles across eligibility phases through this diagram\footnote{According to the \href{www.prisma-statement.org/}{PRISMA} statement for reporting meta-analyses and systematic reviews}. The column to the right depicts the amount of articles excluded in each phase, and the one to the left shows the number of records evaluated.

\bigskip

```{tikz tikz-ex, echo=FALSE, cache=FALSE, eval=TRUE, engine.opts = list(template = "tikz2pdf.tex")}
\usetikzlibrary{shapes.arrows,arrows.meta,positioning,shapes.geometric}
  \begin{tikzpicture} [node distance = 2.7cm, xshift = 1.5]

  \footnotesize
  \linespread{1.0}

  \node (ID) [stage, rotate = 90, yshift = 2cm, xshift = 2.5cm] {\normalsize{Identification}};

  \node (SC) [stage, below of = ID, rotate = 90] {\normalsize{Screening}};

  \node (EL) [stage, below of = SC, rotate = 90] {\normalsize{Eligibility}};

  \node (INC) [stage2, below of = EL, rotate = 90, xshift = -1.2cm] {\normalsize{Included}};

  \node (id) [phase, right of = ID, xshift = 1cm] {Records identified through webscraping  \\ \textbf{(n = 2664)}};

  \node (1st) [exc, right of = id, xshift = 3cm] {Records in languages other than English, book chapters, doctoral theses, and duplicates excluded \\ \textbf{(n = 1220)}};

  \node (screen) [phase, below of = id] {Records screened \\ \textbf{(n = 1445)}};

  \node (2nd) [exc, right of = screen, xshift = 3cm] {Records excluded after reading title and abstract \\ \textbf{(n = 1069)}};

  \node (elig) [phase, below of = screen] {Full-text articles assessed for Eligibility \\ \textbf{(n = 376)}};

  \node (3rd) [exc, right of = elig, xshift = 3cm] {Non-quantitative studies or records using unrelated variables excluded \\ \textbf{(n = 329)}};

  \node (inc_1) [phase, below of = elig] {Preliminary included articles \\ \textbf{(n = 47)}};

  \node (4th) [exc, right of = inc_1, xshift = 3cm] {Articles excluded during analysis due to nonconforming variables \\ \textbf{(n = 21)}};

\node (inc_2) [phase, below of = inc_1] {Included articles \\ \textbf{(n = 26)}};
  \draw [arrow] (id) -- (1st);
  \draw [arrow] (id) -- (screen);
  \draw [arrow] (screen) -- (2nd);
  \draw [arrow] (screen) -- (elig);
  \draw [arrow] (elig) -- (3rd);
  \draw [arrow] (elig) -- (inc_1);
  \draw [arrow] (inc_1) -- (4th);
  \draw [arrow] (inc_1) -- (inc_2);

 \end{tikzpicture}

@@

@@

### Published?

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Was the study published?"}
dat %>%
  ggplot(aes(x = as.factor(published))) + 
    geom_bar(color = "black") + 
  labs(x = "Published study?",
       y = "") + 
  theme_bw()
```

### Dependent variables

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Dependent variables across the law of 1/n studies"}
dat %>%
  mutate(depvar2 = factor(depvar2, 
                          labels = c("Per Capita Expenditure",
                                     "Percentage GDP Government Expenditure",
                                     "Log Per Capita Expenditure"))) %>%
  ggplot(aes(x = depvar2)) +
    geom_bar(color = "black") + 
  labs(x = "Dependent Variables",
       y = "") + 
  coord_flip() + 
  theme_bw()
```

### Independent variables

@@

### Histogram Coefficients

```{r, echo=FALSE}
dat %>%
  ggplot(aes(x = coef)) +
  geom_histogram(bins = 15, color = "black") + 
  labs(x = "Coefficients") + 
  theme_bw()
```

### Histogram Standard Errors

```{r, echo=FALSE}
dat %>%
  ggplot(aes(x = SE)) +
  geom_histogram(bins = 10, color = "black") + 
  labs(x = "Standard Errors") + 
  theme_bw()
```

### Sign Coefficients

```{r, echo=FALSE, fig.width=7, fig.height=6, fig.cap="Coefficient Sign"}
dat %>%
  ggplot(aes(x=as.factor(scoef))) + 
  geom_bar(color = "black") + 
  labs(x = "Coefficient Sign",
       y = "") +
  theme_bw()
```

### Descriptive Statistics of Moderators

We used XXXX

```{r, echo=F,warning=F,message=F}
fulldat$usemeta2 <- factor(fulldat$usemeta)
levels(fulldat$usemeta2) <- c('Other Coefficients', 'Main Coefficients')
aux <- select(fulldat, usemeta2, indepvar2, year, published, 
              elecsys2, method, agglevel, location2) %>%
  rename(`Independent Variables` = indepvar2,
         `Year` = year, 
         `Published work` = published, 
         `Electoral system` = elecsys2, 
         `Estimation method` = method, 
         `Sampling Aggregation Level` = agglevel, 
         `Sample Location` = location2)

export2md(descrTable(~.-usemeta2, aux, y = aux$usemeta2, 
                        show.p.overall = F, show.all = T),
          caption = "Descriptive Statistics of Moderators")
```

### Binomial Tests for Coefficient Sigs

A general test of the theory would be to study whether the coefficients are positive or negative. Note that the law of 1/n poses that we should have a positive influence of legislature size on expenditure. To test this theory, we run a Binomial One-Proportion Z-test. The test consists in contrasting the number of occurences of positive and negative signs (Binomial trials) against the hypothesis that they were produced with 0.5 percent chance. Note that if this is the case, any detected difference would be a mere XXXX of chance.

For the number of legislators in the lower house (N), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='N')
binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
```

Therefore, the most elementary test we could run, a sign direction test, tells us that the law of 1/n does not hold for our sample. For the log of the number of legislators in the lower house (log(N)), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='logN')
binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
```

For log(N), although most coefficients were negative, there are very few studies, making the Finally, for the number of legislators in the upper house (K), the results follow below.

```{r, echo=FALSE}
aux <- filter(dat, indepvar2=='K')
binom.test(table(aux$scoef)[2], sum(table(aux$scoef)), p=0.5, alternative = 'greater')
```

@@

### Electoral system

@@

### Electoral system x Sign Coefficient

@@

### ExpPC x K

@@

```{r, echo=FALSE, fig.width=20, fig.height=5, warning=F,message=F}

@@

magick::image_write(p_full,"figure 1.png")
```

@@

magick::image_write(p_full,"figure 2.png")
```

## Meta-regressions

@@

```{r, echo=FALSE}
mod <- permutest(mod, progbar = F)

@@

```{r, echo=F, warning=F,error=F,message=F}
coefs <- tibble(
  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
)

aux <- list(mod3, mod4, mod5, mod6, mod1, mod2) %>%
  map(~{
    left_join(coefs, .x) %>%
      mutate(model = ifelse(is.na(model), model[1], model)) 
  }) %>%
  reduce(bind_rows) %>%
    mutate(
         order = ifelse(` ` == "Intercept", 1, NA),
         order = ifelse(` ` == "Indepvar: N", 2, order),
         order = ifelse(` ` == "Indepvar: logN", 3, order),
         order = ifelse(` ` == "Year", 4, order),
         order = ifelse(` ` == "Published: No", 5, order),
         order = ifelse(` ` == "Elecsys: Non-Majoritarian", 6, order),
         order = ifelse(` ` == "Method: Panel", 7, order),
         order = ifelse(` ` == "Method: IV", 8, order),
         order = ifelse(` ` == "Method: RDD", 9, order),
         order = ifelse(` ` == "AggLevel: States", 10, order),
         order = ifelse(` ` == "Location: World", 11, order)) %>%
  arrange(order) %>%
  mutate_at(vars(contains("Value")), list(
    ~ifelse(is.na(.), " ", ifelse(. < 0.001, "***",
                       ifelse(. < 0.01, "**",
                              ifelse(. < 0.05, "*", 
                                     ifelse(. < 0.10, ".", " ")))))
      )) %>%
  mutate_at(vars(contains("Estimate") | contains("SE")),
            list(~ifelse(is.na(.), " ", .))) %>%
  mutate(SE = paste0("(", SE,")",`P-Value`)) %>%
  mutate(SE = ifelse(grepl("^\\( ",SE), " ", SE)) %>%
  select(-`T`,-CI,-`P-Value`,-order) %>%
  pivot_longer(cols = c("Estimate", "SE")) %>%
  pivot_wider(names_from = model, values_from = c(value)) %>%
  select(-name)

@@

## Summary of Results

```{r, echo=F, warning=F,error=F,message=F,asis=T}
kable(aux, 
      booktabs = T,
      longtable = F,
      align = "c",
      linesep ='',
      col.names = c(
        " ",
        "Base",
        "Full",
        "Base",
        "Full",
        "Base",
        "Full"
      )) %>% 
  collapse_rows(1:2,row_group_label_position ='identity',
                latex_hline = "none") %>%
  add_header_above(c(" ","ExpPC" = 2, "logExpPC" = 2, "PCTGDP" = 2)) %>%
  kable_styling(
    c("striped",
      "bordered", 
      "scale_down",
      "repeat_header",
      "full_width"
      ),
    position = "center",
    latex_options = c("repeat_header")) %>%
  footnote(general = "Signif. codes:  0 ‘***’ 0.001 ‘**’ 0.01 ‘*’ 0.05 ‘.’ 0.1 ‘ ’ 1")

@@

## Summary of Results (Permutation)

```{r, echo=F, warning=F,error=F,message=F}
coefs <- tibble(
  ` ` = c("Intercept", "Indepvar: N","Indepvar: logN", "Year", "Published: No", "Elecsys: Non-Majoritarian",
    "Method: Panel", "Method: IV", "Method: RDD", "AggLevel: States", "Location: World")
)
